\section{Ricardian model}
\label{sec:Ricardo}
The model of Costinot et al.(2011) is set up as follows. The world economy consists of  $i = 1, \dots, n$ countries and $k = 1, \dots , K $ industries. Further, labour is the only factor of production, which is perfectly mobile across industries and immobile between countries. $L_i $ denotes the number of workers in each country $i$  and $ w_i $ denotes their wage. \par %technology
The authors model the production technology as follows.  Each industry produces a good with a constant returns to scale technology. Further, each good there are indefinitely many varieties $\omega \in \Omega$. \par
Assumption 1. Stochastic productivity differences. The fundamental productivity $z_i^k(\omega)$, which denotes how much of a variety $\omega$ may be produced with one unit of labor,  is for each triple of country, industry and variety $(i,k,\omega)$ a random draw from the Fr{\'e}chet distribution. Therefore \[ F^k_i (z) = exp [-(z/z^{k}_i )^{-\theta} ] \] \par
Assumption 2. Iceberg transport cost. Of every unit of a good, which is shipped form industry $k$ in country $i$ to country $j$ only a fraction $1/d^k_{i,j} \leq 1$ arrives. Further the authors assume that for a third country $l$ importing a good $k$ from country $i$ through $j$ is more costly than directly importing it. Thus $d^k_{i,l} \leq d^k_{i,j} d^k_{j,l} $ for any third country $l$. \par
Assumption 3. Market Structure. It is assumed that the market structure is perfect competition. The consumers therefore pay a price equal to the lowest combination of production and transport cost. \[p^k_j(\omega)=\min_{1\leq i \leq I} {c_{i,j}^k(\omega)} \] with the unit production cost are equal to $c^k_{i,j}=\frac{d^k_{i,j} w_i}{z_i^k}$ . \par
Assumption 4. Consumer preferences. The consumer preferences are modeled with a  two-tier utility function. The upper-tier is a Cobb-Douglas function and lower tier CES function. 
The choice of the CES function implies that the consumer show a 'love-for-variety' property. The consumer welfare with this utility function increases monotonically with the number of goods  for a given level of expenditures on goods and a given price of a variety   \textcite[p. 118]{helpman}. The assumed structure of consumer preferences implies the following relation for the total expenditure of any country $j$ on a variety $\omega$ of a good $k$. 
\begin{align*}
x^k_{j}(\omega) &=  \left(\frac{ p^k_{j}(\omega) }  {  \left( \sum_{\omega' \in \Omega} {p_j^k (\omega')}^{1-\sigma_j^k } \right)^{1/(1-\sigma_j^k) }}    \right)\, \alpha^k_j \,Y_j \quad \text{where} 0 \leq \alpha_j^k < 1,\sigma_{j}^k<1+\theta \quad \text{and} \, \\
\end{align*}
Therefore  expenditure depends on the pattern of relative prices and the share of income it spends on the particular good. 
% Further I define $p^k_{j} =  {  \left( \sum_{\omega' \in \Omega} {p_k^j (\omega')}^{1-\sigma_j^k } \right)}^{1/(1-\sigma_j^k) } $  \par
[From here Important]
Under the outlined assumptions it follows that bilateral trade satisfies the following relation \begin{align} x^k_{i,j}= \frac{(c^k_{i,j})^{ -\theta} } {\sum_{i'=1}^{I}(c^k_{i',j})^{-\theta } }  \alpha^k_j Y_j \quad \text{and}\quad Y_j=w_j  L_j \end{align}
From the relation above  following Lemma, is implied. The first log difference of ${x_{i,j}^k} /x_{i,j}^{k'}$ accounts for differences in wages $w_i$ across exporting countries and incomes $Y_j$ across importing countries. Further, the second log difference $\left({x_{i,j}^k} /x_{i,j}^{k'} \right)  \left({x_{i',j}^k} /x_{i,j}^{k'} \right) $ accounts for differences in the expenditure shares $\alpha^k_j$ across destinations. Therefore the ratio of relative exports of country $i$ and $i'$ to country $j$ in industry $k$ and $k'$ is determined by the relative ratio of productivity and the relative ratio of trade cost. Therefore the model  makes Ricardian prediction at the industry level. 
\begin{align} \ln \left( \frac{{x}_{i,j}^k {x}^{k'}_{i',j}}{{x}_{i,j}^{k'} {x}^{k}_{i',j}} \right) = \theta \ln \left( \frac{{z}_{i}^k {z}^{k'}_{i'}}{{z}_{i}^{k'} {z}^{k}_{i'}} \right)--\theta \ln \left( \frac{ d_{ij}^k d^{k'}_{i',j}}{d_{i,j}^{k'} {d}^{k}_{i',j}} \right) \end{align}

\section{Empirical predictions}
However the prediction above is based on fundamental productivity based prediction, which can not be empirically observed.  To allow the application of the prediction of the model empirically, a link between fundamental and observed productivity is necessary. \par \textcite{costinot} show that from assumption 1 the ratio of observed productivity $\tilde{z}^k_i / \tilde{z}^k_{i'}$ for a country pair $i$ and $i'$ multiplied by the ratio of openness of country $i$ and $i'$  scaled by the exponent one divided by $\theta$ links directly to the ratio of fundamental productivity, based on this insight the showed the following theorem. \par 
\begin{align} \ln \left( \frac{\tilde{x}_{i,j}^k \tilde{x}^{k'}_{i'j}}{\tilde{x}_{i,j}^{k'} \tilde{x}^{k}_{i'j}} \right) = \theta \ln \left( \frac{\tilde{z}_{i}^k \tilde{z}^{k'}_{i'}}{\tilde{z}_{i}^{k'} \tilde{z}^{k}_{i'}} \right)--\theta \ln \left( \frac{ d_{ij}^k d^{k'}_{i'j}}{d_{i,j}^{k'} {d}^{k}_{i'j}} \right) \end{align}
The relation above links openness corrected exports $\tilde{x}_{i,j}^k$ to the observed productivity and trade cost. The first ratio of  $\frac{\tilde{x}_{i,j}^k} { \tilde{x}_{i', j}^{k'} }$ clears the model of differences in income $Y_j$ of importing countries and wages $w_i$ across exporting countries. Further the second ratio $(\frac{\tilde{x}_{i,j}^k}{\tilde{x}^{k'}_{i'j}})/ \frac{tilde{x}^{k}_{i'j}}{\tilde{x}^{k'}_{i'j}}) $clears the relation of differences in the expenditure shares $\alpha^k$ for different industries among importers $j$. Therefore the authors showed that observed productivity links to openness corrected exports.  \par 
The productivity term in \cref{eq:1} is net of specific trade barriers $\delta_{i,j}$ between country $i$ and $j$ like distance and net of trade barriers $\delta_j^k$ specific imposed by the importing country$j$ on the $k$ goods \footnote{The latter fixed-effect include as well  trade protection in line with the most-favorite nation (MFN) clause of the WTO \parencite{costinot}. The MFN clause is that a country can not offer less favorable conditions to a party e.g. an investor of an agreement than to any other investor in the same specific matter from a third country  \parencite{oecd-mfn}.}. Further the error term $\epsilon^k_{i,j}$ includes variable trade cost and other components.
\par 
Further to empirically apply the model above, the measure of observed productivity has to be specified. In their Ricardo setup
the authors showed that the observed ratio of relative productivity is fully reflected in the inverse ratio of producer price indices. Therefore the authors  specify productivity as the inverse of producer prices. This result holds in the Ricardo world, however in the context of international product fragmentation, producer prices as well include foreign contributions.
\par
The authors showed that econometrically equivalent instead of the log linear model above a simpler version may be used for the empirical analysis.
  \begin{align} \label{eq:1} \ln \tilde{x}_{i,j}^k=\delta_{i,j}+\delta_j^k + \theta \ln\tilde{z}_i^k+\epsilon^k_{i,j} \end{align}  
The \cref{eq:1} states that the openness corrected exports  $\tilde{x}_{i,j}^k \equiv x_{i,j}^k -  \tilde{\pi}_{i,i} $ from industry $k$ in exporting country $i$ to importing country $j$ are predicted by the observed productivity $\ln\tilde{z}_i^k$,  exporter-importer fixed-effects $\delta_{i,j}$ and importer-industry fixed-effects $\delta_j^k$. \textcite{costinot} interpret the equation as an analogue to a 'difference-in-difference' estimation. 
The productivity term in \cref{eq:1} is net of specific trade barriers $\delta_{i,j}$ between country $i$ and $j$ like distance and net of trade barriers $\delta_j^k$ specific imposed by the importing country$j$ on the $k$ goods \footnote{The latter fixed-effect include as well  trade protection in line with the most-favorite nation (MFN) clause of the WTO \parencite{costinot}. The MFN clause is that a country can not offer less favorable conditions to a party e.g. an investor of an agreement than to any other investor in the same specific matter from a third country  \parencite{oecd-mfn}.}. Further the error term $\epsilon^k_{i,j}$ includes variable trade cost and other components. \par
Further, structural RCA measure is obtained as follows. The first equation  . The second equation restates the equation with the full set of fixed effects.
   \begin{align} \label{eq:2}\ln {x}_{i,j}^k=\delta_{i,j}+\delta_j^k + \theta \ln{z}_i^k
+\epsilon^k_{i,j} \\
\ln {x}_{i,j}^k=\delta_{i,j}+\delta_j^k + \delta_i^k + \epsilon^k_{i,j} \end{align}
The $\delta_i^k$ in the second relation captures the effect of  $\theta \ln{z}_i^k$ on the bilateral gross exports. 
  \[ z^k_i=e^{{\delta_i^ k}/{\theta}} \] 
\section{Generalization}
However, the simple relation becomes more complex if one generalized the cost function such that several production factors e.g. intermediate inputs and capital are used in different shares in each industry. The motivation behind this generalization is that the literature of international fragmentation of production emphasizes the importance of trade in intermediaries. \par
I will show the I use a cost function similar to Shikher (2011).  \[ c^k_{i,j}=\frac{d^k_{i,j}}{z_{i}^k Y_j} w^{\alpha^k}_i r^{\beta^k}_i \rho^{1-\alpha^k-\beta^k}_{i} \]. Further, I assume that the industries mix intermediate inputs in fixed proportions. The price of inputs $\rho_i$ is therefore a Cobb-Douglas function of industry prices:
\[\rho_{i}= \prod\limits_{m=1}^{K}  p^{\eta_{i,m}}_{i}  \] where $\eta_{i,m} \geq 0$ is the share of industry $m$ goods in the intermediate inputs of industry $k$, such that $\sum_{m=1}^K \eta_{i,m}=1, \forall i$.  For this more general cost function the bilateral trade flows would know depend on the production factor usage in the industries and the usage of input factor prices. The ranking of countries based on the model specific productivity factor would now be confunded by the effects of different factor endowments.  
\par From this general cost function we may still arrive at the relation in theorem if one assumes that the share of production factor used in the production of a good  is not industry specific. Therefore the cost function simplifies as follows  \[ c^k_{i,j}=\frac{d^k_{i,j}}{z_{i}^k } w^{\alpha}_i r^{\beta}_i \rho^{1-\alpha-\beta}_{i} \]. where
$\rho_{i}= \prod\limits_{m=1}^{K}  p^{\eta_{i,m}}_{i} $ It is clear that the cost function together with equation (1) and assumption 1 would still imply (2). \par Based on this the question whether the value-added exports affect the  RCA ranking becomes more clear as a test whether the factor shares of the inputs and other production factors are sector specific. Further, it is easy to extend the cost function to include International sourcing of inputs by introducing another subscript to the input production factor.  Similar to the previous explanations about sector specific production factors, the international sourcing pattern would confound the picture of productivity rankings if the sourcing pattern would be sector specific. 
%
%\section{Ricardian model -- version 2}
%\label{sec:Ricardo}
%%The model of \textcite{costinot} generalized the Eaton-Kortum multi-country Ricardo model to a multi-industry setup by moving the heterogeneous stochastic productivity to the level of varieties. The main contribution of  \textcite{costinot} was to derive a consistent theoretical alternative to the measure of revealed comparative advantage from \textcite{Balassa} in a multi-country multi-industry setup with imperfect specialization. \par
%
%In this section I  describe the model of \textcite{costinot}. Further, I discuss a possible generalization of the production structure of this model, which allows to discuss a theoretically framework to study the effect of IPF on the structure of RCA.   \par 
%
%The model of \textcite{costinot} is set up as follows. The world economy consists of  $i = 1, \dots, n$ countries and $k = 1, \dots , K $ industries. Further, labour is the only factor of production, which is perfectly mobile across industries and immobile between countries. $L_i $ denotes the number of workers in each country $i$  and $ w_i $ denotes their wage. \par %technology
%
%The authors model the production technology as follows.  Each industry produces a good with a constant returns to scale technology. Further, each good there are indefinitely many varieties $\omega \in \Omega$. Moreover, $z^k_i(\omega)$ denotes the number of varieties $\omega$ ,which can be produced with one unit of labor in country $i$, industry $k$. This labor productivity is for each country, industry and variety a random draw from the Fr{\'e}chet distribution, which is an extreme value distribution.
%Formally, 
% By the choice of the distribution, two parameters $z^k_{i}$ and $\theta$ summarize the complete production technology differences across countries and industries. \par 
%
%The first term describes the fundamental productivity of industry $k$ in country $i$ due to e.g. climate, infrastructure and institutions, which affect all firms in one country's industry. The variations of $z^k_i$ determine the cross-country differences in relative labor productivity. The second parameter $\theta$ measures intra-industry heterogeneity, which means that it reflects the differences of production know-how across varieties.  Further, $\theta$ is the same for all industries and countries. To highlight the implication of this assumption,
%consider e.g. the productivity in the manufacturing industries 'food and beverages' and 'machinery and equipment'  the assumption implies that  productivity differences in both industries are the same in each country.\par %trade cost % technical assumptions
%
%%Transport Cost
%Additionally, the authors assume transport cost of Samuelson{'}s iceberg form. Therefore of every  unit of a good, which is shipped, a certain share of the value  'melts' away  \parencite[p.78]{combes}. Formally, $1/d^k_{i,j} \leq 1$ units arrive of every shipped unit of the good $k$ from country $i$ in country $j$  %\footnote{ The main motivation of iceberg trade cost is that it facilitates general equilibrium modeling, as it allows to not model the transport industry  \parencite{krugman1998}. Empirically however there is no good reason to   \parencite{krugman1998}.}. 
%\par
%Further the model assumes that the market structure is perfect competition. Therefore the consumer pay the lowest price  for each variety of a good, which is equivalent to the cost of production and the shipping costs. The unit cost of production and delivering are as follows $c^k_{i,j}=\frac{d^k_{i,j} w_i}{z_i^k}$ and the price for consumers in country $j$ .  \par 
%
% Further, the authors assume that no cross-country arbitrage is possible, which means that for a third country $l$, it is more expensive to indirectly import a good from  country $i$ through  country $j$ than to directly import the good.  \par % consumer problem
%The utility function of the representative consumer is a two-tier utility function. The upper-tier utility function is a Cobb-Douglas function.  The lower-tier utility function is a constant elasticity of substitution utility function. Therefore the expenditure of any country $j$ on one variety $\omega$ of a good $k$ are equal to
%
% % \footnote{The constant elasticity assumption implies that opening up to trade has no pro-competitive effects.}, which assumes that all variety are symmetric \textcite[p. 117]{helpman}. 
%The consumer preferences show a 'love-for-variety' property, because the consumer welfare increases monotonically with the number of goods  for a given level of expenditures on goods and a given price of a variety  \textcite[p. 118]{helpman}. The assumption implies that the total expenditure of any country $j$ on a variety of a good depends on the pattern of relative prices and the share of income it spends on the particular good.
%  %preferences
%A final assumption, which closes the model is that  trade is balanced trade across countries. 
%
%%Further to show that their model makes a theoretical prediction of a relation between exports and productivity differences, the authors assume that trade cost between country $i$ industry $k$ and country $j$  can be decomposed into a country pair $\delta_{i,j}$ and destination-industry specific trade cost $\delta^k_j $, therefore $\delta^k_{i,j}=\delta^k_j \delta_{i,j}$. The authors prove that under this assumptions the ranking of fundamental productivity fully determines the ranking of relative exports. 

\endinput